\documentclass[aspectratio=169,11pt]{beamer}
\usetheme{default}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}{%
  \hfill\insertframenumber/\inserttotalframenumber\hspace*{4pt}\vspace{2pt}%
}
\usepackage{lmodern}
\usepackage[most]{tcolorbox}
\usepackage{listings}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,shapes.geometric,fit,backgrounds}
\usepackage{booktabs}
\usepackage{hyperref}

\definecolor{lcgreen}{HTML}{2E7D32}
\definecolor{lcblue}{HTML}{1565C0}
\definecolor{lcorange}{HTML}{EF6C00}
\definecolor{lcred}{HTML}{C62828}
\definecolor{codebg}{HTML}{F5F5F5}
\definecolor{docgray}{gray}{0.55}

\newtcolorbox{conceptbox}[1][]{colback=yellow!20,colframe=yellow!60!black,title=#1,fonttitle=\bfseries,top=2pt,bottom=2pt,left=4pt,right=4pt}
\newtcolorbox{warningbox}[1][]{colback=red!15,colframe=red!60!black,title=#1,fonttitle=\bfseries,top=2pt,bottom=2pt,left=4pt,right=4pt}
\newtcolorbox{tipbox}[1][]{colback=green!10,colframe=green!50!black,title=#1,fonttitle=\bfseries,top=2pt,bottom=2pt,left=4pt,right=4pt}
\newtcolorbox{codebox}[1][]{colback=blue!10,colframe=blue!40!black,title=#1,fonttitle=\bfseries,top=2pt,bottom=2pt,left=4pt,right=4pt}

\lstset{
  basicstyle=\ttfamily\scriptsize,
  backgroundcolor=\color{codebg},
  breaklines=true,
  frame=single,
  rulecolor=\color{blue!40!black},
  keywordstyle=\color{lcblue}\bfseries,
  stringstyle=\color{lcgreen},
  commentstyle=\color{docgray}\itshape,
  language=Python,
  showstringspaces=false,
  tabsize=2,
  xleftmargin=2pt,
  xrightmargin=2pt,
  aboveskip=2pt,
  belowskip=2pt,
}

\newcommand{\docref}[1]{{\scriptsize\color{docgray}[Docs: #1]}}

\title{Section 06: Persistence \& Checkpointing}
\subtitle{Saving State Snapshots for Long-Running Agents}
\author{LangGraph v1.0.x (March 2026)}
\date{}

\begin{document}

\frame{\titlepage}

\begin{frame}{Mental Model: Why Persistence Matters}
  \begin{conceptbox}[The Problem]
    \setlength{\itemsep}{1pt}
    \begin{itemize}
      \item Agents run across \textbf{multiple API calls} (e.g., user messages)
      \item Without persistence, state is \textbf{lost} between invocations
      \item Conversations die, multi-step tasks fail if process crashes
    \end{itemize}
  \end{conceptbox}
  \vspace{0.1cm}
  \begin{conceptbox}[The Solution]
    \setlength{\itemsep}{1pt}
    \begin{itemize}
      \item \textbf{Checkpointing}: save state snapshot after each step
      \item \textbf{Thread IDs}: group related invocations (per user, per conversation)
      \item Combine them: resume exactly where you left off
    \end{itemize}
  \end{conceptbox}
\end{frame}

\begin{frame}{What Is a Checkpointer?}
  \begin{conceptbox}[Checkpointer Definition]
    \setlength{\itemsep}{1pt}
    \begin{itemize}
      \item Object that \textbf{saves state} after each super-step
      \item Implements \texttt{get}, \texttt{put}, \texttt{list} methods
      \item Can be in-memory, SQLite, PostgreSQL, or custom
      \item Enables \textbf{time travel}: read state at any checkpoint
    \end{itemize}
  \end{conceptbox}
  \vspace{0.1cm}
  \begin{tipbox}[Checkpoint Timing]
    Checkpoints happen between graph steps, not inside nodes (that's too frequent).
  \end{tipbox}
\end{frame}

\begin{frame}[fragile]{MemorySaver: In-Memory Checkpointer}
  \begin{codebox}[Development Setup]
    \begin{lstlisting}
from langgraph.checkpoint.memory import MemorySaver
checkpointer = MemorySaver()
graph = builder.compile(checkpointer=checkpointer)
config = {"configurable": {"thread_id": "user_123"}}
result = graph.invoke(
  {"messages": [HumanMessage("Hi")]},
  config=config
)
    \end{lstlisting}
  \end{codebox}
  \vspace{0.1cm}
  \begin{warningbox}[Development Only]
    MemorySaver loses data on process restart. Use only for prototyping.
  \end{warningbox}
\end{frame}

\begin{frame}[fragile]{Setting Up Checkpointing}
  \begin{codebox}[Checkpointer Setup Pattern]
    \begin{lstlisting}
from langgraph.checkpoint.memory import MemorySaver
from langgraph.graph import StateGraph
checkpointer = MemorySaver()
builder = StateGraph(MessagesState)
builder.add_node("agent", agent_node)
builder.add_edge(START, "agent")
graph = builder.compile(checkpointer=checkpointer)
    \end{lstlisting}
  \end{codebox}
  \vspace{0.1cm}
  \begin{tipbox}[Key Parameter]
    \texttt{checkpointer=} in \texttt{compile()} activates persistence.
  \end{tipbox}
\end{frame}

\begin{frame}[fragile]{Thread IDs: Organizing Conversations}
  \begin{codebox}[Thread ID Pattern]
    \begin{lstlisting}
user_id = "user_123"
thread_id = f"conv_{user_id}_{timestamp}"
config = {
  "configurable": {
    "thread_id": thread_id
  }
}
result = graph.invoke(
  {"messages": [HumanMessage("Hello")]},
  config=config
)
    \end{lstlisting}
  \end{codebox}
  \vspace{0.1cm}
  \begin{tipbox}[Thread Strategy]
    One thread per conversation. Group related messages under same thread\_id.
  \end{tipbox}
\end{frame}

\begin{frame}[fragile]{Resuming Conversations}
  \begin{codebox}[Resume from Last Checkpoint]
    \begin{lstlisting}
config = {"configurable": {"thread_id": "conv_123"}}
result_1 = graph.invoke(
  {"messages": [HumanMessage("What's 2+2?")]},
  config=config
)
result_2 = graph.invoke(
  {"messages": [HumanMessage("And 3+3?")]},
  config=config
)
    \end{lstlisting}
  \end{codebox}
  \vspace{0.1cm}
  \begin{tipbox}[Automatic Resumption]
    LangGraph automatically loads last state from thread. New input appends to messages.
  \end{tipbox}
\end{frame}

\begin{frame}[fragile]{Getting State: Inspect Current Checkpoint}
  \begin{codebox}[Retrieve Current State]
    \begin{lstlisting}
config = {"configurable": {"thread_id": "conv_123"}}
state = graph.get_state(config)
print(state.values)
print(state.next)
    \end{lstlisting}
  \end{codebox}
  \vspace{0.1cm}
  \begin{tipbox}[Use Cases]
    Debugging, monitoring agent progress, checking decision points.
  \end{tipbox}
\end{frame}

\begin{frame}[fragile]{Updating State: Modify Externally}
  \begin{codebox}[Manual State Update]
    \begin{lstlisting}
config = {"configurable": {"thread_id": "conv_123"}}
new_state = {
  "messages": state.values["messages"] + [
    HumanMessage("Additional context")
  ]
}
graph.update_state(config, new_state)
result = graph.invoke(None, config)
    \end{lstlisting}
  \end{codebox}
  \vspace{0.1cm}
  \begin{tipbox}[Manual Edits]
    Useful for injecting human feedback or correcting mistakes.
  \end{tipbox}
\end{frame}

\begin{frame}[fragile]{State History: Time Travel}
  \begin{codebox}[View All Checkpoints]
    \begin{lstlisting}
config = {"configurable": {"thread_id": "conv_123"}}
history = graph.get_state_history(config)
for i, state_snapshot in enumerate(history):
  print(f"Checkpoint {i}: {state_snapshot.values}")
  print(f"Next node: {state_snapshot.next}")
    \end{lstlisting}
  \end{codebox}
  \vspace{0.1cm}
  \begin{tipbox}[Debugging and Auditing]
    See entire execution trace. Useful for understanding why agent made a decision.
  \end{tipbox}
\end{frame}

\begin{frame}[fragile]{SqliteSaver: Persistent Local Storage}
  \begin{codebox}[SQLite Checkpointer]
    \begin{lstlisting}
from langgraph.checkpoint.sqlite import SqliteSaver
checkpointer = SqliteSaver(
  conn=sqlite3.connect(".langgraph.db")
)
graph = builder.compile(checkpointer=checkpointer)
    \end{lstlisting}
  \end{codebox}
  \vspace{0.1cm}
  \begin{tipbox}[Local Persistence]
    Data survives process restarts. Perfect for single-machine deployments.
  \end{tipbox}
\end{frame}

\begin{frame}[fragile]{PostgresSaver: Production-Grade Persistence}
  \begin{codebox}[PostgreSQL Checkpointer]
    \begin{lstlisting}
from langgraph.checkpoint.postgres import PostgresSaver
conn_string = "postgresql://user:pass@localhost/langgraph"
async with await asyncpg.create_pool(
  conn_string
) as pool:
  checkpointer = PostgresSaver(
    sync_connection=pool
  )
  graph = builder.compile(checkpointer=checkpointer)
    \end{lstlisting}
  \end{codebox}
  \vspace{0.1cm}
  \begin{tipbox}[Enterprise Ready]
    Distributed, scalable, supports concurrent access. Use for production.
  \end{tipbox}
\end{frame}

\begin{frame}{TikZ Diagram: Checkpoint Flow}
  \begin{center}
    \begin{tikzpicture}[scale=0.85, every node/.style={font=\scriptsize}]
      \node[draw, rectangle, fill=lcblue!20, minimum width=1.2cm, minimum height=0.5cm] (inv) at (0, 2) {Invoke};
      \node[draw, rectangle, fill=lcgreen!20, minimum width=1.2cm, minimum height=0.5cm] (n1) at (1.8, 2) {Node 1};
      \node[draw, rectangle, fill=lcorange!20, minimum width=1.4cm, minimum height=0.5cm] (ckpt1) at (3.6, 2) {Checkpoint};
      \node[draw, rectangle, fill=lcgreen!20, minimum width=1.2cm, minimum height=0.5cm] (n2) at (5.4, 2) {Node 2};
      \node[draw, rectangle, fill=lcorange!20, minimum width=1.4cm, minimum height=0.5cm] (ckpt2) at (7.2, 2) {Checkpoint};
      \draw[-Latex] (inv) -- (n1);
      \draw[-Latex] (n1) -- (ckpt1);
      \draw[-Latex] (ckpt1) -- (n2);
      \draw[-Latex] (n2) -- (ckpt2);
    \end{tikzpicture}
  \end{center}
  \vspace{0.1cm}
  \begin{tipbox}[Pattern]
    Checkpoint after each node executes. Enables resumption from any point.
  \end{tipbox}
\end{frame}

\begin{frame}{Super-Steps Explained}
  \begin{conceptbox}[Super-Step Definition]
    \setlength{\itemsep}{1pt}
    \begin{itemize}
      \item One \textbf{atomic unit} of graph execution
      \item Executes \textbf{all edges from START} to first blocking node
      \item Gets checkpointed after completion
      \item LangGraph waits for human/external input between super-steps
    \end{itemize}
  \end{conceptbox}
  \vspace{0.1cm}
  \begin{tipbox}[Concurrency]
    Super-steps are the natural unit for parallelization and interrupts.
  \end{tipbox}
\end{frame}

\begin{frame}{Thread Management Patterns}
  \begin{conceptbox}[Per-User Pattern]
    \setlength{\itemsep}{1pt}
    \begin{itemize}
      \item One thread per user: \texttt{thread\_id = f"user\_{user\_id}"}
      \item All conversations with that user share one thread
      \item Simpler, but context can get long
    \end{itemize}
  \end{conceptbox}
  \vspace{0.1cm}
  \begin{conceptbox}[Per-Conversation Pattern]
    \setlength{\itemsep}{1pt}
    \begin{itemize}
      \item One thread per conversation: \texttt{thread\_id = f"conv\_{conv\_id}"}
      \item Separate contexts, easier to manage
      \item Recommended for most multi-turn systems
    \end{itemize}
  \end{conceptbox}
\end{frame}

\begin{frame}{Common Pitfalls}
  \begin{warningbox}[Forgetting thread\_id]
    \setlength{\itemsep}{1pt}
    \begin{itemize}
      \item All invocations go to same (anonymous) thread
      \item Conversations pollute each other's state
      \item Solution: always pass \texttt{config=\{"configurable": \{"thread\_id": ...\}\}}
    \end{itemize}
  \end{warningbox}
  \vspace{0.1cm}
  \begin{warningbox}[Stale State]
    \setlength{\itemsep}{1pt}
    \begin{itemize}
      \item Reading state before all nodes finish
      \item Solution: let graph complete, then read from checkpoint
    \end{itemize}
  \end{warningbox}
  \vspace{0.1cm}
  \begin{warningbox}[Large State Objects]
    \setlength{\itemsep}{1pt}
    \begin{itemize}
      \item Storing huge arrays/files in checkpoints
      \item Solution: reference external storage, keep state lean
    \end{itemize}
  \end{warningbox}
\end{frame}

\begin{frame}[fragile]{Summary: Persistence Cheat Sheet}
  \begin{codebox}[Quick Reference]
    \begin{lstlisting}
from langgraph.checkpoint.memory import MemorySaver
checkpointer = MemorySaver()
graph = builder.compile(checkpointer=checkpointer)
config = {"configurable": {"thread_id": "conv_123"}}
result = graph.invoke(input_state, config=config)
state = graph.get_state(config)
history = graph.get_state_history(config)
graph.update_state(config, new_values)
    \end{lstlisting}
  \end{codebox}
\end{frame}

\begin{frame}{Self-Check: Do You Understand?}
  \begin{enumerate}
    \setlength{\itemsep}{1pt}
    \item Why is persistence critical for multi-turn conversations?
    \item What's the difference between MemorySaver and SqliteSaver?
    \item How do thread IDs organize checkpoints?
    \item What happens when you invoke the same thread\_id twice?
    \item How do you inspect the state history?
    \item What's a super-step and when do checkpoints happen?
    \item When should you use per-user vs per-conversation threads?
  \end{enumerate}
\end{frame}

\end{document}
